Community Analysis

### 2022-09-16 Manuscript/manuscript.Rmd
remove packages no longer used and update renv lockfile

```{r initialize-packages}
library(tidyverse)
library(broom)
library(broman)
library(morris)
library(phyloseq)
library(ggpubr)
library(knitr)
library(corncob)
library(ggthemes)
#library(microViz)
library(captioner)
library(knitr)
library(kableExtra)
library(flextable)
library(ggtext)
figures <- captioner()
tables <- captioner(prefix = "Table")
```

>>>>

```{r initialize-packages}
library(tidyverse)
library(broom)
library(broman)
library(morris)
# library(phyloseq)
library(ggpubr)
library(knitr)
library(corncob)
# library(ggthemes)
library(captioner)
library(knitr)
library(ggtext)
figures <- captioner()
tables <- captioner(prefix = "Table")
```

### 2022-09-16 R/08-community-analysis.Rmd
remove packages no longer used and update renv lockfile

library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggthemes)
library(broom)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)

>>>>

library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(broom)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)
